\thesistitle

### 2019-08-17 sections/background.tex
Results

\section{Code clone terminology}\label{sec:terminology}
% The sets are actually definitions, NOT PROPERTIES. This should be clearer.
Many studies present different definitions for code clone concepts. For this study, we mainly use the definitions from Bruntink et al. \cite{bruntink2005use}, Roy et al. \cite{roy2007survey} and Jiang et al. \cite{jiang2007deckard}. We created a summary of these concepts, which can be found in Table~\ref{tab:clone-terminology}.

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllll@{}}
\toprule
\rowcolor[HTML]{FFFFFF}
\textbf{Symbol} & \textbf{Meaning} & \textbf{Definition} & \textbf{Description} & \textbf{Properties} \\ \midrule
\rowcolor[HTML]{EFEFEF}
T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} The range this token\\spans.\\ \textbf{Category (C):} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
N & Node \cite{jiang2007deckard} & Set of tokens. & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} The range this node\\spans.\end{tabular} \\
\rowcolor[HTML]{EFEFEF}
I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{File (F):} The file in which this\\clone instance is found.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
C & Clone class \cite{bruntink2005use, roy2007survey}& \begin{tabular}[c]{@{}l@{}}Set of clone\\instances.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations. Each of these\\code fragments is called a\\``clone instance''.\end{tabular} & - \\
\rowcolor[HTML]{EFEFEF}
S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\classes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & - \\
\rowcolor[HTML]{FFFFFF}
%R & Range & A part of a source code file. &  & \begin{tabular}[c]{@{}l@{}}\textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
 \bottomrule
\end{tabular}%
}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}

>>>>

\section{Code clone terminology}\label{sec:terminology}
Many studies present different definitions for code clone concepts. For this study, we mainly use the definitions from Bruntink et al. \cite{bruntink2005use}, Roy et al. \cite{roy2007survey} and Jiang et al. \cite{jiang2007deckard}. We created a summary of these concepts, which can be found in Table~\ref{tab:clone-terminology}.

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllll@{}}
\toprule
\rowcolor[HTML]{FFFFFF}
\textbf{Symbol} & \textbf{Meaning} & \textbf{Definition} & \textbf{Description} & \textbf{Properties} \\ \midrule
\rowcolor[HTML]{EFEFEF}
T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} The range this token\\spans.\\ \textbf{Category (C):} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
N & Node \cite{jiang2007deckard} & Set of tokens. & \begin{tabular}[c]{@{}l@{}}A statement or declaration node\\in the AST of a codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} The range this node\\spans.\end{tabular} \\
\rowcolor[HTML]{EFEFEF}
I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{File (F):} The file in which this\\clone instance is found.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
C & Clone class \cite{bruntink2005use, roy2007survey}& \begin{tabular}[c]{@{}l@{}}Set of clone\\instances.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations. Each of these\\code fragments is called a\\``clone instance''.\end{tabular} & - \\
\rowcolor[HTML]{EFEFEF}
S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\classes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & - \\
\rowcolor[HTML]{FFFFFF}
%R & Range & A part of a source code file. &  & \begin{tabular}[c]{@{}l@{}}\textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
 \bottomrule
\end{tabular}%
}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}
